DNNNNR0: How to Avoid OOTA Without Really Trying

### 2025-03-27 paper/ootavacuous.tex
ootavacuous: Sharpen Section 7.4 community-process wording
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Although it is unexpected, and while we don't recommend this sort of code
transformation, we cannot say that this conclusion is definitely wrong,
because our intuitive notions of semantic dependency are not clear in
cases where multiple loads of the same variable are present.
% Can we instead say that transforming the code might require that the
% witness also be transformed?
In the unlikely event that this transformation proves useful, there will be
a community process that determines whether this transformation is valid,
that is, whether value of the use cases is worth the added conceptual load
on developers.
Until that time, it is impossible to say whether or not there is
a semantic dependency from \co{y} to \co{z} without reference to a
specific implementation.

>>>>

Although this is unexpected, and while we don't recommend this sort of
code transformation, we cannot say that this conclusion is definitely
wrong, because one's intuitive notions of semantic dependency are not
always clear in cases involving multiple loads from the same variable.
% Can we instead say that transforming the code might require that the
% witness also be transformed?
In the unlikely event that this transformation proves useful, there
will be a community process that determines whether the value of this
transformation is worth the added conceptual load on developers.
Until that time, pure mathematics cannot help us because it is simply
impossible to say whether or not there is a semantic dependency from
\co{y} to \co{z} without reference to a specific implementation.
